Gozde and Liora Extension Project

### 2015-05-12 response_to_reviewers.Rmd

---
title: "response_to_reviewers"
author: "Gozde and Liora"
date: "5/12/2015"
output: html_document
---

We thank all four reviewers for providing excellent feedback on our replication and extension code. Most of their suggestions were related to improving our code, which we adopted whenever possible. Our reviewers also commented on the theoretical and modelling decisions in our code, and we tried to address these points below.

Replication Edits:

1) Following Aaron and Andres's recommendation, we used pipes in our data cleaning code, specifically in the code to rename a number of variables in the data frame (lines 41-58). Since we didn't change all 83 variable names, the "rename" function rather than dplyr's "select" command  was more practical. This change made our code much more simple to edit and easier to follow through. 
2) As per Aaron and Andres's suggestion, we added documentation on the packages we are using in our replication. 
3) We agree with Angela and Matt's comments on the hard-coded numbers for centered variables (lines 67-69): We acknowledge that this is not good coding practice; however, due to our difficulty in reading the author's original code in Stata, we were unable to reproduce these numbers via our own code in R. Our efforts to find how the author calculated grand-mean centering for these two variables could not yield these results so we used the hard-coded numbers.
4) Per Matt and Angela's suggestions, we have created a function to plot all four of the graphs.  In addition to making the code somewhat more concise, this makes our code more self-documenting in that it highlights the similar structures of these graphs.

Extension Edits:

1) We improved our logit link function in line with Matt's comment (line 93): we gave better names for arguments and outputs; we removed redundant code which created the link function for each model. 
2) Following Matt's suggestion (line 95), we graphed the range in predicted probabilities to better present the very little variation in predictions for all three models. The differences between the graphs for each model also made us realize the connection between plotted probabilities and the separation plots. 
3) Per Andres's comment (line 144) about the use of interactions in model 3, we added furher documentation. Here we decided to use interactions between contextual variables following the author's original model. 
4) Following Matt's question about the multi-level model, we added a note on this point. While we were interested in visualizing the predictive power of all three theories in our extension, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze extreme-right vote intention for each individual.

### 2015-05-12 extension.Rmd
updated with more edits

#Conclusion
There isn't a big range in the predicted probabilities of the model, therefore the predicted probabilities are not very helpful. Separation plot helps a lot to discern the predictive power of the model. As the events of extreme right vote intension increases as we move to the right (i.e. red lines cluster around the end of the graph), the model does a good job of estimating the likelihood of events. However, as the small arrow in the graph shows, the model predicts that half the number of observations will have the intention to vote for an extreme right party. The number of actual events (red lines) is much lower.

```

@@

```

@@

>>>>

#Conclusion
There isn't a big range in the predicted probabilities of the model, therefore the predicted probabilities are not very helpful. Separation plot helps a lot to discern the predictive power of the model. As the events of extreme right vote intension increases as we move to the right (i.e. red lines cluster around the end of the graph), the model does a good job of estimating the likelihood of events. However, as the small arrow in the graph shows, the model predicts that half the number of observations will have the intention to vote for an extreme right party. The number of actual events (red lines) is much lower.  
```

@@

@@

This extension breaks Arzheimer's multi-level model into three different models that correspond to the three theoretical explanations for political orientation towards extreme right parties and movements. While we were interested in visualizing the predictive power of each theory, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze ER vote intension. That said, we think treating each country as another level that the election contexts are nested in (rather than taking countries as dummy variables) would have provided an even more compelling multi-level model.
